Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field

### 2024-05-08 paper/ms.tex
update ms

\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
  %
  \item The age distributions of both the Kepler target stars and the
    known Kepler planet-hosts show a demographic cliff.  There are
    \ratioobtoybstars\ times as many ``old'' (2-3\,Gyr) stars in the
    Kepler field as ``young'' (0-1\,Gyr) stars.  The star formation
    rate today is \ratiosfr$\pm$\uncratiosfr\ times lower than it was
    three billion years ago.
    This star formation history broadly agrees with those derived
    from CMD fitting and white-dwarf chronology, though with
    important nuances.
  %
  \item Rather than expecting $\approx$500 exoplanets younger than one
    billion years, this rotation-based age distribution of stars in the
    Kepler field implies that we should instead expect $\approx$250.
  %
  %FIXME: 120 number
  \item Using rotation-based ages, we have derived ages for
    \nplyounggyrotwosigma\ Kepler planets younger than 1\,Gyr at 2$\sigma$,
    and \nplyounggyro\ planets with median ages below 1\,Gyr.
    Concatenating these planets against the existing literature yields
    $\approx$120-170 known sub-gigayear planets with well-constrained
    ages.  This lessens the original factor of ten discrepancy to
    a factor of at most two.
\end{enumerate}

>>>>

\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
  %
  \item The age distributions of both the Kepler target stars and the
    known Kepler planet-hosts show a demographic cliff.  There are
    \ratioobtoybstars\ times as many ``old'' (2-3\,Gyr) stars in the
    Kepler field as ``young'' (0-1\,Gyr) stars.  The star formation
    rate today is \ratiosfr$\pm$\uncratiosfr\ times lower than it was
    three billion years ago.
    This star formation history broadly agrees with those derived
    from CMD fitting and white-dwarf chronology, though with
    important nuances.
  %
  \item Rather than expecting $\approx$500 exoplanets younger than one
    billion years, the age distribution of stars in the
    Kepler field implies that we should instead expect $\approx$250.
  %
  %FIXME: 120 number
  \item Using rotation-based ages, we have derived ages for
    \nplyounggyrotwosigma\ Kepler planets younger than 1\,Gyr at 2$\sigma$,
    and \nplyounggyro\ planets with median ages below 1\,Gyr.
    Concatenating these planets against the existing literature yields
    $\approx$120-170 known sub-gigayear planets with well-constrained
    ages.  This lessens the original factor of ten discrepancy to
    a factor of at most two.
\end{enumerate}
